Beta to Release Matching: Modeling

### 2020-03-10 poc/matchIt/modeling.Rmd
update the modeling

library(kableExtra)      # help you build common complex tables and manipulate table styles
library(DataExplorer)    # automated data exploration
library(tidyverse)       # for general data wrangling (includes readr and dplyr)
library(ggplot2)         # to draw statistical plots 
library(ggthemes)
library(funModeling) 
library(corrplot)
library(MatchIt)
library(optmatch)
library(RItools)
library(magrittr)
library(tidyr)
library(tidyselect)
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
## Loading the training dataset

load("~/GitHub/ff-beta-release-matching/poc/EDA/data_milestone2_df_train_validate_20191025.RData")
```

```{r echo=FALSE}
## Examine data briefly

kable(introduce(df_train_f)) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
scroll_box(width = "100%")
```

```{r}
f <- freq(df_train_f$label)

levels(df_train_f$label) <- c(FALSE,TRUE)
df_train_f$label <- as.logical(df_train_f$label)
```

@@

* 302,819 observations: 59,627 beta ("treated") and 243,192 release ("control")
* Covariants: 
  + Environment
      - cpu_cores
      - cpu_cores_cat
      - cpu_speed_mhz
      - cpu_speed_cat
      - cpu_vendor
      - cpu_l2_cache_kb
      - cpu_l2_cache_kb_cat
      - memory_mb
      - memory_cat
      - os_version
      - is_wow64
      - distro_id_norm
      - install_year
  + Geo
      - country
      - timezone_offset
      - timezone_cat
      - locale
  + Settings
      - num_bookmarks
      - num_addons
      - sync_configured
      - fxa_configured
      - is_default_browser
      - default_search_engine
  + Page Load
      - FX_PAGE_LOAD_MS_2_PARENT
      - TIME_TO_DOM_COMPLETE_MS
      - TIME_TO_DOM_CONTENT_LOADED_END_MS
      - TIME_TO_LOAD_EVENT_END_MS
      - TIME_TO_DOM_INTERACTIVE_MS
      - TIME_TO_NON_BLANK_PAINT_MS
  + Startup
      - startup_ms
      - startup_ms_max
  + Stability
      - content_crashes
  + Browser engagement
      - active_hours
      - active_hours_max
      - uri_count
      - uri_count_max
      - search_count
      - search_count_max
      - num_pages
      - num_pages_max
      - daily_max_tabs
      - daily_max_tabs_max
      - daily_unique_domains
      - daily_unique_domains_max
      - daily_tabs_opened
      - daily_tabs_opened_max
  + Frequency of Browser Usage
      - num_active_days
      - daily_num_sessions_started
      - daily_num_sessions_started_max
      - session_length
      - session_length_max
      - profile_age
      - profile_age_cat

```{r}
df_release <- df_train_f %>% filter(label == TRUE)
df_beta <- df_train_f %>% filter(label == FALSE)
```

```{r}
# sampling for beta overrepresentation
n_beta <- nrow(df_beta)
build_df <- function(multiple){
  df <- df_release %>%
    sample_n(size = round(n_beta / multiple)) %>%
    rbind(df_beta)
}

@@

```{r}
f <- freq(as.factor(df_1x_sm$label)) # ~ 50% - 50%
f <- freq(as.factor(df_2x_sm$label)) # ~ 70% - 30%
f <- freq(as.factor(df_4x_sm$label)) # ~ 80% - 20%
```

@@

environment <- c('cpu_cores','cpu_speed_mhz','cpu_l2_cache_kb','memory_mb','timezone_offset','num_bookmarks','num_addons')

@@

@@

The standardized difference can be used to compare the mean of continuous and binary variables between treatment groups. The standardized difference compares the difference in means in units of the pooled standard deviation and allows for the comparison of the relative balance of variables measured in different units. Although there is no universally agreed-upon criterion as to what threshold of the standardized difference can be used to indicate an important imbalance, a standard difference that is less than $0.1$ has been taken to indicate a negligible difference in the mean or prevalence of a covariate between treatment groups.

### 1x Oversampling
```{r}
cov <- df_1x_sm %>% select(c(engagement, usage, environment, page_load, startup, stability))
treated <- (df_1x_sm$label==FALSE)
std.diff <- apply(cov,2,function(x) 100*(mean(x[treated])- mean(x[!treated]))/(sqrt(0.5*(var(x[treated]) + var(x[!treated])))))
sort(abs(std.diff))
```

### 2x Oversampling
```{r}
cov <- df_2x_sm %>% select(c(engagement, usage, environment, page_load, startup, stability))
treated <- (df_2x_sm$label==FALSE)
std.diff <- apply(cov,2,function(x) 100*(mean(x[treated])- mean(x[!treated]))/(sqrt(0.5*(var(x[treated]) + var(x[!treated])))))
sort(abs(std.diff))
```

### 4x Oversampling
```{r}
cov <- df_4x_sm %>% select(c(engagement, usage, environment, page_load, startup, stability))
treated <- (df_4x_sm$label==FALSE)
std.diff <- apply(cov,2,function(x) 100*(mean(x[treated])- mean(x[!treated]))/(sqrt(0.5*(var(x[treated]) + var(x[!treated])))))
sort(abs(std.diff))
```

@@

* As we can see, all standardized differences at the individual variable level were greater than *0.1*. These significant imbalances highlight the need for an effective matching strategy to create a release group that more closely resembles the beta group.
* For the standardized difference, absolute scores higher than *25%* are considered suspect, and may indicate an imbalance for that specific variable.
  + That is, `TIME_TO_DOM_INTERACTIVE_MS`, `TIME_TO_DOM_COMPLETE_MS`, `TIME_TO_LOAD_EVENT_END_MS`, `timezone_offset`, `num_addons` and `session_length` (only for the 2x Oversampling).

## 2. Check initial balance

The package [RItools](https://cran.r-project.org/web/packages/RItools/index.html) includes the routine `XBalance` that estimates a chi-square test to which checks if there is at least one variable in the selection model for which the two groups are different.

* *How similar are treatment/control groups on X?*

### 1x Oversampling
```{r}
xBalance(label ~ (active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes), data=df_1x_sm, report=c("chisquare.test"))
```

### 2x Oversampling
```{r}
xBalance(label ~ (active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes), data=df_2x_sm, report=c("chisquare.test"))
```

### 4x Oversampling
```{r}
xBalance(label ~ (active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes), data=df_4x_sm, report=c("chisquare.test"))
```

* A statistically significant chi-square will indicate that at least one of the variables included in the model is creating an imbalance between the two groups. Variables that create imbalance should be included in the selection model.

## 3. Propensity Score Estimation

@@

```{r}
ps <- glm(label ~ active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes, data=df_1x_sm, family=binomial())
summary(ps)
```

@@

```{r}
df_1x_sm$psvalue <- predict(ps, type="response")
```

## Back to back histogram

```{r fig.height=5, fig.width=10}
out <- histbackback(split(df_1x_sm$psvalue, df_1x_sm$label), main="Propensity score before matching", xlab=c("release", "beta"))
#! just adding color
barplot(-out$left, col="#111d5e" , horiz=TRUE, space=0, add=TRUE, axes=FALSE)
barplot(out$right, col="#b21f66", horiz=TRUE, space=0, add=TRUE, axes=FALSE)
```

@@

```{r}
ps <- glm(label ~ active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes, data=df_2x_sm, family=binomial())
summary(ps)
```

@@

```{r}
df_2x_sm$psvalue <- predict(ps, type="response")
```

## Back to back histogram

```{r fig.height=5, fig.width=10}
out <- histbackback(split(df_2x_sm$psvalue, df_2x_sm$label), main="Propensity score before matching", xlab=c("release", "beta"))
#! just adding color
barplot(-out$left, col="#111d5e" , horiz=TRUE, space=0, add=TRUE, axes=FALSE)
barplot(out$right, col="#b21f66", horiz=TRUE, space=0, add=TRUE, axes=FALSE)
```

@@

```{r}
ps <- glm(label ~ active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes, data=df_4x_sm, family=binomial())
summary(ps)
```

@@

```{r}
df_4x_sm$psvalue <- predict(ps, type="response")
```

## Back to back histogram

```{r fig.height=5, fig.width=10}
out <- histbackback(split(df_4x_sm$psvalue, df_4x_sm$label), main="Propensity score before matching", xlab=c("release", "beta"))
#! just adding color
barplot(-out$left, col="#111d5e" , horiz=TRUE, space=0, add=TRUE, axes=FALSE)
barplot(out$right, col="#b21f66", horiz=TRUE, space=0, add=TRUE, axes=FALSE)
```

@@

## 4. Propensity Score Matching

### Match using Coarsened Exact Matching (CEM)

@@

```{r}
m.cem <- matchit(label ~ active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes, data=df_1x_sm, method="cem")
summary(m.cem)
m.cem.1 = match.data(m.cem)
```

```{r fig.height=5, fig.width=10}
plot(m.cem, type = "jitter", col = "#111d5e")
```

```{r fig.height=5, fig.width=10}
plot(m.cem, type = "hist", col = "#111d5e")
```

@@

```{r}
m.cem <- matchit(label ~ active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes, data=df_2x_sm, method="cem")
summary(m.cem)
m.cem.2 = match.data(m.cem)
```

```{r fig.height=5, fig.width=10}
plot(m.cem, type = "jitter", col = "#111d5e")
```

```{r fig.height=5, fig.width=10}
plot(m.cem, type = "hist", col = "#111d5e")
```

@@

```{r}
m.cem <- matchit(label ~ active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes, data=df_4x_sm, method="cem")
summary(m.cem)
m.cem.4 = match.data(m.cem)
```

```{r fig.height=5, fig.width=10}
plot(m.cem, type = "jitter", col = "#111d5e")
```

```{r fig.height=5, fig.width=10}
plot(m.cem, type = "hist", col = "#111d5e")
```

### Match using Nearest Neighbor matching

@@

```{r}
m.nn <- matchit(label ~ active_hours + active_hours_max + uri_count + uri_count_max + search_count + search_count_max + num_pages + num_pages_max + daily_max_tabs + daily_max_tabs_max + daily_unique_domains + daily_unique_domains_max + daily_tabs_opened + daily_tabs_opened_max + num_active_days + daily_num_sessions_started + daily_num_sessions_started_max + session_length + session_length_max + profile_age + cpu_cores + cpu_speed_mhz + cpu_l2_cache_kb + memory_mb + num_bookmarks + FX_PAGE_LOAD_MS_2_PARENT + TIME_TO_DOM_CONTENT_LOADED_END_MS + TIME_TO_NON_BLANK_PAINT_MS + startup_ms + startup_ms_max + content_crashes, data=df_1x_sm, method="nearest", replace = TRUE)
summary(m.nn)
m.nn.1 = match.data(m.nn)
```

```{r fig.height=5, fig.width=10}
plot(m.nn, type = "jitter", col = "#111d5e")
```

```{r fig.height=5, fig.width=10}
plot(m.nn, type = "hist", col = "#111d5e")
```

@@

* What we want to see is that the Matched Treated (beta) and Matched Control (release) distributions are roughly similar. So, we can do better.

## 5. Computing indices of covariate imbalance after matching

### 1x Oversampling

#### CEM

>>>>

library(kableExtra)      # help you build common complex tables and manipulate table styles
library(DataExplorer)    # automated data exploration
library(tidyverse)       # for general data wrangling (includes readr and dplyr)
library(ggplot2)         # to draw statistical plots 
library(dplyr)           # for data frame manipulation
library(ggthemes)
library(funModeling) 
library(corrplot)
library(MatchIt)
library(optmatch)
library(cem)
library(RItools)
library(magrittr)
library(tidyr)
library(tidyselect)
library(grt)
library(tableone)
```

```{r echo=TRUE, message=FALSE, warning=FALSE}
## Loading the training dataset
#load("~/GitHub/ff-beta-release-matching/poc/EDA/data_milestone2_df_train_validate_20191025.RData")
load('~/ff-beta-release-matching/poc/matchIt/feature_selection.RData')
```

```{r include=FALSE}
colnames(df_train_encoder)[which(names(df_train_encoder) == "cpu_l2_cache_kb_cat_< 1024")] <- "cpu_l2_cache_kb_cat_l1024"
colnames(df_train_encoder)[which(names(df_train_encoder) == "cpu_l2_cache_kb_cat_< 256")] <- "cpu_l2_cache_kb_cat_l256"
colnames(df_train_encoder)[which(names(df_train_encoder) == "cpu_l2_cache_kb_cat_< 512")] <- "cpu_l2_cache_kb_cat_l512"
colnames(df_train_encoder)[which(names(df_train_encoder) == "cpu_l2_cache_kb_cat_> 1024")] <- "cpu_l2_cache_kb_cat_g1024"

colnames(df_train_encoder)[which(names(df_train_encoder) == "default_search_engine_other (bundled)")] <- "default_search_engine_other_bundled"
colnames(df_train_encoder)[which(names(df_train_encoder) == "default_search_engine_other (non-bundled)")] <- "default_search_engine_other_nonbundled"

colnames(df_train_encoder)[which(names(df_train_encoder) == "locale_en-GB")] <- "locale_enGB"
colnames(df_train_encoder)[which(names(df_train_encoder) == "locale_en-US")] <- "locale_enUS"

colnames(df_train_encoder)[which(names(df_train_encoder) == "timezone_cat_[-12,-10]")] <- "timezone_cat_m12_m10"
colnames(df_train_encoder)[which(names(df_train_encoder) == "timezone_cat_(-10,-8]")] <- "timezone_cat_m10_m8"
colnames(df_train_encoder)[which(names(df_train_encoder) == "timezone_cat_(-8,-6]")] <- "timezone_cat_m8_m6"
colnames(df_train_encoder)[which(names(df_train_encoder) == "timezone_cat_(-6,-4]")] <- "timezone_cat_m6_m4"
colnames(df_train_encoder)[which(names(df_train_encoder) == "timezone_cat_(-4,-2]")] <- "timezone_cat_m4_m2"
colnames(df_train_encoder)[which(names(df_train_encoder) == "timezone_cat_(-2,0]")] <- "timezone_cat_m2_0"
colnames(df_train_encoder)[which(names(df_train_encoder) == "timezone_cat_(0,2]")] <- "timezone_cat_0_2"
colnames(df_train_encoder)[which(names(df_train_encoder) == "timezone_cat_(2,4]")] <- "timezone_cat_2_4"
colnames(df_train_encoder)[which(names(df_train_encoder) == "timezone_cat_(4,6]")] <- "timezone_cat_4_6"
colnames(df_train_encoder)[which(names(df_train_encoder) == "timezone_cat_(6,8]")] <- "timezone_cat_6_8"
colnames(df_train_encoder)[which(names(df_train_encoder) == "timezone_cat_(8,10]")] <- "timezone_cat_8_10"
colnames(df_train_encoder)[which(names(df_train_encoder) == "timezone_cat_(10,12]")] <- "timezone_cat_10_12"
colnames(df_train_encoder)[which(names(df_train_encoder) == "timezone_cat_(12,14]")] <- "timezone_cat_12_14"
```

```{r include=FALSE}
generate_formula <- function(tr_cov, label){
  # Focus on linear and no-interactions
  return(as.formula(paste(label, '~', paste(tr_cov, collapse="+"))))
}

calc_means <- function(df.match, ho_cov, add_1 = FALSE){
  # Validation
  ## Means: holdout
  ho_mean <- df.match %>% 
    select(ho_cov, label) %>% 
    mutate_all(function(x) if(is.numeric(x) && add_1) x+1 else x) %>%
    group_by(label) %>% 
    summarise_all(mean)
  return(ho_mean)
}

calc_medians <- function(df.match, ho_cov, add_1 = FALSE){
  # Validation
  ## medians: holdout
  ho_median <- df.match %>% 
    select(ho_cov, label) %>% 
    mutate_all(function(x) if(is.numeric(x) && add_1) x+1 else x) %>%
    group_by(label) %>% 
    summarise_all(median)
  # print(ho_median)
  # return(list(train = tr_median, ho = ho_median))
  return(ho_median)
}

calc_delta <- function(df.match, ho_cov){
  perc_diff <- function(x) abs(x[1]-x[2])/x[2]
  means <- calc_means(df.match, ho_cov) %>%
    select(-label) %>% 
    summarise_all(perc_diff)
  medians <- calc_medians(df.match, ho_cov) %>%
    select(-label) %>% 
    summarise_all(perc_diff)
  # return(list(means = means, medians = medians))
  df <- means %>% 
    rbind(medians) %>% 
    as.data.frame() %>%
    set_rownames(c('means', 'medians'))
  return(df)
}
```

```{r echo=FALSE}
# define response field
label <- 'is_release'

## Examine data briefly
kable(introduce(df_train_encoder)) %>%
kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F) %>%
scroll_box(width = "100%")
```

```{r}
f <- freq(df_train_encoder$label_beta)
```

@@

* $302,819$ observations: $59,627$ beta ("treated") and $243,192$ release ("control")
* $95$ covariants: 
  + Environment
      - cpu_cores
      - cpu_cores_cat
      - cpu_speed_mhz
      - cpu_speed_cat
      - cpu_vendor
      - cpu_l2_cache_kb
      - cpu_l2_cache_kb_cat
      - memory_mb
      - memory_cat
      - os_version
      - is_wow64
      - distro_id_norm
      - install_year
  + Geo
      - country
      - timezone_offset
      - timezone_cat
      - locale
  + Settings
      - num_bookmarks
      - num_addons
      - sync_configured
      - fxa_configured
      - is_default_browser
      - default_search_engine
  + Page Load
      - FX_PAGE_LOAD_MS_2_PARENT
      - TIME_TO_DOM_COMPLETE_MS
      - TIME_TO_DOM_CONTENT_LOADED_END_MS
      - TIME_TO_LOAD_EVENT_END_MS
      - TIME_TO_DOM_INTERACTIVE_MS
      - TIME_TO_NON_BLANK_PAINT_MS
  + Startup
      - startup_ms
      - startup_ms_max
  + Stability
      - content_crashes
  + Browser engagement
      - active_hours
      - active_hours_max
      - uri_count
      - uri_count_max
      - search_count
      - search_count_max
      - num_pages
      - num_pages_max
      - daily_max_tabs
      - daily_max_tabs_max
      - daily_unique_domains
      - daily_unique_domains_max
      - daily_tabs_opened
      - daily_tabs_opened_max
  + Frequency of Browser Usage
      - num_active_days
      - daily_num_sessions_started
      - daily_num_sessions_started_max
      - session_length
      - session_length_max
      - profile_age
      - profile_age_cat

```{r}
df_beta <- df_train_encoder %>% filter(label_beta == 1)
df_rel <- df_train_encoder %>% filter(label_beta == 0)
```

```{r}
# sampling for beta overrepresentation
n_beta <- nrow(df_beta)
build_df <- function(multiple){
  df <- df_rel %>%
    sample_n(size = round(n_beta / multiple)) %>%
    rbind(df_beta)
}

@@

```{r}
f <- freq(as.factor(df_1x_sm$label_beta)) # ~ 50% - 50%
f <- freq(as.factor(df_2x_sm$label_beta)) # ~ 70% - 30%
f <- freq(as.factor(df_4x_sm$label_beta)) # ~ 80% - 20%
```

@@

environment <- c('cpu_cores','cpu_speed_mhz','cpu_vendor_AMD','cpu_vendor_Intel','cpu_vendor_Other','cpu_l2_cache_kb','cpu_l2_cache_kb_cat_l1024','cpu_l2_cache_kb_cat_l256','cpu_l2_cache_kb_cat_l512','cpu_l2_cache_kb_cat_g1024','memory_mb','is_wow64_True','distro_id_norm_acer','distro_id_norm_Mozilla','distro_id_norm_other','distro_id_norm_Yahoo','install_year')

geo <- c('country_US','timezone_offset','timezone_cat_m12_m10','timezone_cat_m10_m8','timezone_cat_m8_m6','timezone_cat_m6_m4','timezone_cat_m4_m2','timezone_cat_m2_0','timezone_cat_0_2','timezone_cat_2_4','timezone_cat_4_6','timezone_cat_6_8','timezone_cat_8_10','timezone_cat_10_12','timezone_cat_12_14','locale_enGB','locale_enUS')

settings <- c('num_bookmarks','num_addons','sync_configured_True','fxa_configured_True','is_default_browser_True','default_search_engine_Bing','default_search_engine_DuckDuckGo','default_search_engine_Google','default_search_engine_other_bundled','default_search_engine_other_nonbundled','default_search_engine_Yahoo')

@@

## Variable Selection
The Boruta method was performed.

## Experiments
Groups of models to train.

```{r}
exp_1 <- c('daily_num_sessions_started', 'daily_num_sessions_started_max', 'FX_PAGE_LOAD_MS_2_PARENT', 'fxa_configured_True', 'memory_mb', 'num_active_days', 'num_addons', 'num_bookmarks', 'profile_age','session_length','session_length_max','TIME_TO_DOM_COMPLETE_MS','TIME_TO_DOM_CONTENT_LOADED_END_MS','TIME_TO_DOM_INTERACTIVE_MS','TIME_TO_LOAD_EVENT_END_MS','TIME_TO_NON_BLANK_PAINT_MS','timezone_cat_0_2')

exp_2 <- c('country_US', 'daily_num_sessions_started', 'daily_num_sessions_started_max', 'default_search_engine_other_nonbundled', 'FX_PAGE_LOAD_MS_2_PARENT', 'fxa_configured_True', 'memory_mb', 'num_active_days', 'num_addons', 'num_bookmarks', 'profile_age', 'session_length','session_length_max', 'startup_ms', 'startup_ms_max', 'sync_configured_True', 'TIME_TO_DOM_COMPLETE_MS','TIME_TO_DOM_CONTENT_LOADED_END_MS','TIME_TO_DOM_INTERACTIVE_MS','TIME_TO_LOAD_EVENT_END_MS','TIME_TO_NON_BLANK_PAINT_MS','timezone_cat_0_2')

exp_3 <- c('daily_num_sessions_started', 'daily_num_sessions_started_max', 'FX_PAGE_LOAD_MS_2_PARENT', 'memory_mb', 'num_active_days', 'num_addons', 'num_bookmarks', 'profile_age', 'session_length', 'session_length_max','TIME_TO_DOM_COMPLETE_MS','TIME_TO_DOM_CONTENT_LOADED_END_MS','TIME_TO_DOM_INTERACTIVE_MS','TIME_TO_LOAD_EVENT_END_MS','TIME_TO_NON_BLANK_PAINT_MS')

exp_4 <- c('cpu_speed_mhz', 'daily_num_sessions_started', 'daily_num_sessions_started_max', 'default_search_engine_other_nonbundled', 'FX_PAGE_LOAD_MS_2_PARENT', 'memory_mb', 'num_active_days', 'num_addons', 'num_bookmarks', 'profile_age','session_length','session_length_max','startup_ms','startup_ms_max','TIME_TO_DOM_COMPLETE_MS','TIME_TO_DOM_CONTENT_LOADED_END_MS','TIME_TO_DOM_INTERACTIVE_MS','TIME_TO_LOAD_EVENT_END_MS','TIME_TO_NON_BLANK_PAINT_MS')
```

@@

The standardized difference can be used to compare the mean of continuous and binary variables between treatment groups. The standardized difference compares the difference in means in units of the pooled standard deviation and allows for the comparison of the relative balance of variables measured in different units. Although there is no universally agreed-upon criterion as to what threshold of the standardized difference can be used to indicate an important imbalance, a standard difference that is less than 10% (or $0.1$) has been taken to indicate a negligible difference in the mean or prevalence of a covariate between treatment groups.

### 1x Oversampling
```{r message=FALSE, warning=FALSE}
cov <- df_1x_sm %>% dplyr::select(c(engagement, usage, environment, geo, settings, page_load, startup, stability))
treated <- (df_1x_sm$label_beta == 1)
std.diff <- apply(cov,2,function(x) 100*(mean(x[treated])- mean(x[!treated]))/(sqrt(0.5*(var(x[treated]) + var(x[!treated])))))
cov_df_1x <- sort(abs(std.diff))
cov_df_1x
```

### 2x Oversampling
```{r}
cov <- df_2x_sm %>% dplyr::select(c(engagement, usage, environment, geo, settings, page_load, startup, stability))
treated <- (df_2x_sm$label_beta == 1)
std.diff <- apply(cov,2,function(x) 100*(mean(x[treated])- mean(x[!treated]))/(sqrt(0.5*(var(x[treated]) + var(x[!treated])))))
cov_df_2x <- sort(abs(std.diff))
cov_df_2x
```

### 4x Oversampling
```{r}
cov <- df_4x_sm %>% dplyr::select(c(engagement, usage, environment, geo, settings, page_load, startup, stability))
treated <- (df_4x_sm$label_beta == 1)
std.diff <- apply(cov,2,function(x) 100*(mean(x[treated])- mean(x[!treated]))/(sqrt(0.5*(var(x[treated]) + var(x[!treated])))))
cov_df_4x <- sort(abs(std.diff))
cov_df_4x
```

@@

* As we can see, all standardized differences at the individual variable level were greater than *0.1* (except for the `timezone_cat_10_12`,`timezone_cat_m10_m8`,`cpu_l2_cache_kb_cat_l512` variables). These significant imbalances highlight the need for an effective matching strategy to create a release group that more closely resembles the beta group. Variables that create imbalance *should* be included in the selection model:

```{r}
exp_5  <- c(setdiff(names(cov_df_1x[3:73]), engagement))
exp_6  <- c(setdiff(names(cov_df_2x), engagement)) 
exps <- list(exp_1 = exp_1, exp_2 = exp_2, exp_3 = exp_3, exp_4 = exp_4, exp_5 = exp_5, exp_6 = exp_6)
```

## 2. Propensity Score Estimation

@@

```{r, collapse=TRUE}
ps_1x <- list()
for (exp in names(exps)){
  ps <- glm(generate_formula(exps[[exp]], label), data=df_1x_sm, family=binomial())
  ps_1x[[exp]] <- ps
  print(summary(ps))
}
```

@@

```{r fig.height=7, fig.width=14}
par(mfrow=c(2,3))
for (ps in ps_1x){
  df_1x_sm$psvalue <- predict(ps, type="response")
  out <- histbackback(split(df_1x_sm$psvalue, df_1x_sm$label_release), main="Propensity score before matching", xlab=c("release", "beta"))
  # just adding color
  barplot(-out$left, col="#111d5e" , horiz=TRUE, space=0, add=TRUE, axes=FALSE)
  barplot(out$right, col="#b21f66", horiz=TRUE, space=0, add=TRUE, axes=FALSE)
}
```

@@

```{r, collapse=TRUE}
ps_2x <- list()
for (exp in names(exps)){
  ps <- glm(generate_formula(exps[[exp]], label), data=df_2x_sm, family=binomial())
  ps_2x[[exp]] <- ps
  print(summary(ps))
}
```

@@

```{r fig.height=7, fig.width=14}
par(mfrow=c(2,3))
for (ps in ps_2x){
  df_2x_sm$psvalue <- predict(ps, type="response")
  out <- histbackback(split(df_2x_sm$psvalue, df_2x_sm$label_release), main="Propensity score before matching", xlab=c("release", "beta"))
  # just adding color
  barplot(-out$left, col="#111d5e" , horiz=TRUE, space=0, add=TRUE, axes=FALSE)
  barplot(out$right, col="#b21f66", horiz=TRUE, space=0, add=TRUE, axes=FALSE)
}
```

@@

```{r, collapse=TRUE}
ps_4x <- list()
for (exp in names(exps)){
  ps <- glm(generate_formula(exps[[exp]], label), data=df_4x_sm, family=binomial())
  ps_4x[[exp]] <- ps
  print(summary(ps))
}
```

@@

```{r, fig.height=7, fig.width=14}
par(mfrow=c(2,3))
for (ps in ps_4x){
  df_4x_sm$psvalue <- predict(ps, type="response")
  out <- histbackback(split(df_4x_sm$psvalue, df_4x_sm$label_release), main="Propensity score before matching", xlab=c("release", "beta"))
  # just adding color
  barplot(-out$left, col="#111d5e" , horiz=TRUE, space=0, add=TRUE, axes=FALSE)
  barplot(out$right, col="#b21f66", horiz=TRUE, space=0, add=TRUE, axes=FALSE)
}
```

@@

## 3. Propensity Score Matching

### Match using Coarsened Exact Matching (CEM): Small Dataset

@@

```{r, collapse=TRUE}
cem_results_1x <- list()
cem_models_1x <- list()
for (exp in names(exps)){
  cem <- matchit(formula = generate_formula(exps[[exp]], label), df_1x_sm, 'cem')
  res <- match.data(cem)
  cem_models_1x[[exp]] <- cem
  cem_results_1x[[exp]] <- res
  #print(summary(cem))
}
```

@@

```{r, collapse=TRUE}
cem_results_2x <- list()
cem_models_2x <- list()
for (exp in names(exps)){
  cem <- matchit(formula = generate_formula(exps[[exp]], label), df_2x_sm, 'cem')
  res <- match.data(cem)
  cem_models_2x[[exp]] <- cem
  cem_results_2x[[exp]] <- res
  #print(summary(cem))
}
```

@@

```{r, collapse=TRUE}
cem_results_4x <- list()
cem_models_4x <- list()
for (exp in names(exps)){
  cem <- matchit(formula = generate_formula(exps[[exp]], label), df_4x_sm, 'cem')
  res <- match.data(cem)
  cem_models_4x[[exp]] <- cem
  cem_results_4x[[exp]] <- res
  #print(summary(cem))
}
```

### Match using Nearest Neighbor matching: Small

@@

```{r, collapse=TRUE}
nn_results_1x <- list()
nn_models_1x <- list()
for (exp in names(exps)){
  nn <- matchit(formula = generate_formula(exps[[exp]], label), df_1x_sm, 'nearest', replace = TRUE)
  res <- match.data(nn)
  nn_models_1x[[exp]] <- nn
  nn_results_1x[[exp]] <- res
  #print(summary(nn))
}
```

@@

* As can be seen from the figures above, there is a notable improvement in the match between the two distributions of propensity scores after the match (compared to the results before to match). This match suggests the two groups (beta and release) are much more similar in terms of their propensity scores and, therefore, the selection bias has been reduced substantially.
